\plaintitle

### 2017-06-16 papers/IoT2017/concl.tex
updates

As the complexity of power systems increases due to the evolution of power grids, decentralized transactive-energy IoT systems are emerging to tackle this complexity.
However, these decentralized systems also give rise to new privacy challenges, which are further complicated by the stringent safety and security requirements of power systems.
We have addressed these challenges by providing a novel solution for anonymous energy trading within a transactive microgrid.
Our solution builds on distributed ledgers, such as blockchains, and other proven techniques for anonymity, such as mixing services and onion routing.
We have described the novel process of anonymous energy trading and detailed the novel transactions and services used in our system.
Finally, we have discussed how the proposed solution satisfies security, safety, and privacy requirements.
In future work, we will provide rigorous proofs of satisfying these requirements, and we will present an implementation of our system with performance results.

>>>>

% Abhishek, as always, it would be best if we could revise this
% summary of the paper's contents to be a summary of lessons learned
% based upon our experiences to date!

As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity.  Ironically, these decentralized systems
also give rise to new privacy challenges, such as ...
% Abhishek, please briefly list the key privacy challenges we cover in
% this paper.
These privacy challenges are exaccerbated by the stringent safety and
security requirements of power systems.

This paper describes how we are addressing these challenges via an
innovative solution for anonymous energy trading within a transactive
microgrid.  Our solution builds on distributed ledgers, such as
blockchains, and other proven techniques for anonymity, such as mixing
services and onion routing.  We described our robust process of
anonymous energy trading and explain the novel transactions and
services used in our system.  Finally, we discussed how the proposed
solution satisfies security, safety, and privacy requirements.  In
future work, we will provide rigorous proofs of satisfying these
requirements, and we will present an implementation of our system with
performance results.
